Dynein project log

### 2016-09-22 thesis_stuff/thesis_stuff.tex
Figure out the Winch paper angle scheme and get a couple more equilibrium angles for thesis_stuff.pdf!

\section{Physical Parameters}
\subsection{Stalk and tail length}
Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and XXXX (pre and post-powerstroke) to find
these values.

@@

\textbf{Physical Parameters from Winch Model paper}:\\
Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when prestroke.

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomograph.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomograph.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}

\end{document}

>>>>

\section{Physical Parameters}

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & &\\ \hline
    $L_t$ &  7nm & & & &\\ \hline
    $R_b$ &  & & & &\\ \hline
    $R_m$ &  7nm & & & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}

---- not sure if the Lin angles are right, since measuring the angle that the tail makes is \textit{not} necessarily the angle the angle the linker makes ----\\

a: Sarlah \textit{et al} gives us two different rate constants which could represent the bothbound to onebound transition: motor dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$). We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound since it is the slower of the two.\\

b: There are several Sarlah \textit{et al} rate constants we could use for the onebound to bothbound rate constant: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$) or the power stroke itself ($k_{PS} = 5000 s^{-1}$). We choose to represent the transition with $k_{-Pi} = 5000 s^{-1}$ because all these rates are fairly similar. We do not want to use the MT-binding rate because it could include both binding kinetics as well as MT-search kinetics, the latter of which we do not want to include in our binding rate.\\

\subsection{Stalk and tail length}
Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and XXXX (pre and post-powerstroke) to find
these values.

@@

\textbf{Physical Parameters from Winch Model paper}:\\
Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm binding angle: 34 degrees from vertical, motor
domain radius: 7nm. Their angle scheme is different than ours in that it has the linker/tail facing towards the MT, which looks different
from our facing-up tail. This might be a confusion on our part in the difference between the linker and the tail, but it may not. By assuming the linker starts at the top of the head and points downwards, we can calculate an estimate for tail length as $L_t = 7nm$.

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}

\subsection{2012 Kon Crystal Structure (3VKH)}
This paper crystallizes a full-length and MTBD-truncation mutants. 3VKH is the full-length, but one MTBD of the dimer did not come out in the crystal structure.

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\item Fix generate-stepping-data non-printing bug.
\end{itemize}
\end{document}
